Similar Sentence Detection Using Locality Sensitive Hashing Technique on Wikipedia

### 2013-11-11 article/article-draft.tex
Removed restrictions on sentence similarity counts

After applying the score to the entire set of wiki clusters (with a score threshold of .6), there are 244,660 template clusters and 906,960 non-template clusters, including 666,212 identical clusters. The template clusters contain 1,116,932 sentences, and the non-template clusters contain 1,244,196.

@@

Based on our preliminary analysis, templatification tends to occur most often between articles that maintain large lists of information related to the same general sub-theme of different topics. For example, the articles ''List of birds of Zambia'' and ''List of birds of Tanzania'' share a large number of templated sentences. With both countries sharing the same geographic region, it is not unexpected that their respective Wikipedia articles on the countrys' bird species would be highly comparable. For clarity purposes, we define \emph{similarity count} as simply the total number of sentences between two articles that were found to share the same hash signature. Using the output of the minhashing routine, we performed a pairwise similarity count across all articles that shared similar sentences. Overall, we found $\approx 29580$ wikipedia article pairs that had a similarity count greater than $50$.

>>>>

After applying the score to the entire set of wiki clusters (with a score threshold of .6), there are 244,660 template clusters and 906,960 non-template clusters, including 666,212 identical clusters. The template clusters contain 1,116,932 sentences, and the non-template clusters contain 1,244,196 sentences.

@@

 For clarity purposes, we define \emph{similarity count} as simply the total number of sentences between two articles that were found to share the same hash signature. Using the output of the minhashing routine, we performed a pairwise similarity count across all articles that shared similar sentences. Overall, we found $\approx 29580$ wikipedia article pairs that had a similarity count greater than $50$.
